The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-29 paper/ms.tex
new subsection on abundance matching

\section{Abundance Matching Methodology}
\label{sec:methodology}

@@

The observed UV Luminosity Function has two slopes. To reproduce it we decide to use the
 four parameter model:
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenBosch03} and the mean relation between
stellar mas of a galaxy and the mass of its halo used by \citet{Moster10}.

>>>>

\section{Theoretical and Numerical Framework}
\label{sec:methodology}

\subsection{The Abundance Matching Methodology}
We use an abundance matching approach to find the relationship between
dark matter halo mass and star formation rate. 
This approach has been used to link stellar and dark matter masses. 
Here we extend it to constraint star formation rate properties at high
redshift.

The starting point for this medho is a population of dark matter halos.
To each halo we assign a UV luminosity according to the following
parameterization.
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1},
  \end{equation}
where $M$ is the DM mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are two slopes corresponding to the faint and
bright end, respectively. 
This equation has the same functional dependence as stellar to dark
mass ratio used by \citet{Moster10}.

@@
